Untitled

### 2024-02-01 Evalsims.Rmd
send

plt1 <- ggplot(results_1 , aes(x = cal_error, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration error of f ($\\n_{Cal} = 1000)"),
                    color = "Sig. Level", linetype = "Sig. Level") +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

plt2 <- ggplot(results_2 , aes(x = n, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration set size ($kappa_{train} = 3$)"), color = "Sig. Level", linetype = "Sig. Level") + scale_x_log10() +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

library(patchwork)
combined_plot <- (plt1 + plt2)  + plot_layout(guides = "collect", axis_titles = "collect", axes = "collect") & theme(legend.position = "bottom") #+  labs(color = TeX("$\\alpha$"), linetype = TeX("$\\alpha$"))
combined_plot
print(combined_plot)

ggsave("plots/calibration_shift_2.pdf", plot = combined_plot, width = 6, height = 4)
# this plot is good

@@

plot1 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot2 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

@@

plot3 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot4 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

@@

plot5 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot6 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

>>>>

plt1 <- ggplot(results_1 , aes(x = cal_error, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration error in f"),
                    color = "Level", linetype = "Level") +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

plt2 <- ggplot(results_2 , aes(x = n, y = relative, color = (alpha), linetype = (alpha))) + geom_line() +
  theme_bw() + labs(y = TeX("Relative Width (cal/uncal)"), x = TeX("Calibration set size"), color = "Level", linetype = "Level") + scale_x_log10() +
  geom_hline(yintercept = 1, color = "black", linetype = "dashed" , alpha = 0.5) + scale_y_continuous(limits = c(0.7, 1.2))

library(patchwork)
combined_plot <- (plt1 + plt2)  + plot_layout(guides = "collect", axis_titles = "collect", axes = "collect") & theme(legend.position = "right") #+  labs(color = TeX("$\\alpha$"), linetype = TeX("$\\alpha$"))
combined_plot
print(combined_plot)

ggsave("plots/calibration_shift_2.pdf", plot = combined_plot, width = 6, height = 3)
# this plot is good

@@

plot1 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot2 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

@@

plot3 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot4 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

@@

plot5 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot6 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Marginal"))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

### 2024-02-01 plot_curves.Rmd
send

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.5.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "isotonic", "method"] <- "SC-CP (ours)"
#data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
#data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "conditional", "method"] <- "Cond-CP"
data[data$method == "marginal", "method"] <- "Uncond-CP"

>>>>

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.6.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "isotonic", "method"] <- "SC-CP (ours)"
#data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
#data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "conditional", "method"] <- "Cond-CP"
data[data$method == "marginal", "method"] <- "Uncond-CP"
